---
title: "MDE KPI Report Q1 2026"
format: html
editor: visual
author: Jalon Howard

last_updated: 04/02/2026
---

## ø. To-Do

## I. Summary

- **Report Name:** Michigan Department of Education (MDE) Report

- **Frequency**: Quarterly

- **Scope**

  - [Timeframe]{.underline}: Previous quarter [and]{.underline} cumulative to-date

  - [Population]{.underline}: Schools that launched (i.e had at least one trainee complete a core training type) under 31p2 contract

- **Output Metrics:**

  - Number of schools implementing TRAILS in any Tier

  - Number of students who gained access to TRAILS resources and supports 

  - Number of staff trained by Tier (can be counted duplicatively and cumulatively)

    - Staff may be counted more than once when participating in more than one tier of programming

- [**Report SOP**](https://docs.google.com/document/d/1TWWRyGJQ6Givl9Z_K5zDSxptdyVxO-EJQgzlj8GnsBo/edit?tab=t.0)

- **Data Sources**

  - [List of MDE Schools]{.underline} -\> Salesforce Contract Implementations with Account info & Core Training Launch Date filtered where contract contains '31p2' and by appropriate date parameters

  - [Trainings by Tier]{.underline} -\> Salesforce Training Affiliations filtered by [List of MDE Schools]{.underline}

  - [Student Access Data]{.underline} -\> [National Center for Education Statistics (NCES) search](https://nces.ed.gov/ccd/schoolsearch/) with the following criteria:

    - State: "Michigan"

    - School Description: "Regular, Special Education, Vocational, Other/Alternative"

### Update to Run

```{r}
# Reporting Period
r_year <- '2026'
r_quarter <- 'Q1'

# Data extraction date
## Format:YYYYMMDD
edate <- '20260414'
```

### Environment

```{r}
library(pacman)
p_load(qualtRics, tidyverse, dplyr, janitor)

p <- paste0(r_year,'_',r_quarter)

dir_in <- paste0('/Users/jalonr77/Documents/Evaluation Projects/JH_Git/data_requests_internal/mde_kpi_report/',p,'/Data/Raw/')
dir_out <- paste0('/Users/jalonr77/Documents/Evaluation Projects/JH_Git/data_requests_internal/mde_kpi_report/',p,'/Data/Out/')
```

### Data In

```{r}
# Files In
file_in_sf_affiliations <- paste0(dir_in,'sf_export_affiliations_31p2_',edate,'.csv')
file_in_sf_31p2_schools <- paste0(dir_in,'sf_export_schools_31p2_',edate,'.csv')
file_in_nces_schools <- paste0(dir_in,'nces_schools_public_mi_24_25_',edate,'.csv')


df_affiliations <- clean_names(read_csv(file_in_sf_affiliations, show_col_types = FALSE))
df_31p2_schools <- clean_names(read_csv(file_in_sf_31p2_schools, show_col_types = FALSE))
df_nces <- clean_names(read_csv(file_in_nces_schools, skip=11, show_col_types = FALSE))
```

### Data Out

```{r}
# Auto-update date suffix for file-out names
date_suff <- str_remove_all(as.character(today()), "-")

# Initialize empty dataframe for Student Access and Implementing Schools KPIs
df_mde_kpi_init <- data.frame(
  kpi_name = character(0),
  tier_1 = numeric(0),
  tier_2 = numeric(0),
  tier_3 = numeric(0),
  any_tier = numeric(0)
  )

# Visual Check
colnames(df_mde_kpi_init)
df_mde_kpi_init
```

```{r}
# Trainee Types
list_trainee_types <- c(
  'T1_Staff',
  'T2_CIT',
  'T2_SMHP',
  'T3_Educator',
  'T3_SMHP',
  'T3_Admin',
  'T3_Both_Admin_SMHP',
  'T3_Community',
  'Any Training'
)

# Initialize empty dataframe for Trainees KPI
df_mde_kpi_trainees <- data.frame(
  mde_role = list_trainee_types,
  current_q = NA,
  cumulative = NA
  )

df_mde_kpi_trainees
```

### Other Data Structures

```{r}
# Dictionary of reporting periods
dict_report_period <- list(
  # Q1: Jan 1-Mar 31
  'Q1' = c('start'= paste0(r_year,'-01-01'), 
           'end'=paste0(r_year,'-03-31')),
  # Q2: Apr 1-Jun 30
  'Q2' = c('start'= paste0(r_year,'-04-01'), 
           'end'=paste0(r_year,'-06-30')),
  # Q3: Jul 1-Sep 30
  'Q3' = c('start'= paste0(r_year,'-07-01'), 
           'end'=paste0(r_year,'-09-30')),
  # Q4: Oct 1-Dec 31
  'Q4' = c('start'= paste0(r_year,'-10-01'), 
           'end'=paste0(r_year,'-12-31'))
)

```

```{r}

# Dictionary of qualifying trainings and corresponding MDE Role
dict_mde_role <- list(
  ## Tier 1 Trainings Topics
  'Curriculum' = 'T1_Staff',

  ## Tier 2 Trainings Topics
  'CBT & Mindfulness' = NA,
  
  ## Tier 3 Trainings Topics
  'ISD/Administrator' = 'T3_Admin', 
  'School Staff' = 'T3_Educator', 
  'SMHP' = 'T3_SMHP', 
  'Community' = 'T3_Community', 
  'Risk Assessment and Management' = 'T3_Both_Admin_SMHP'
)
```

## III. Clean & Wrangle

### NCES School Data

```{r}

df_nces_wrangled <- df_nces %>%
  # Remove NA
  filter(
    !is.na(students)
  ) %>%
  # Update col data type
  mutate(
    students = as.integer(students),
    state_school_id = gsub("[^[:alnum:]]", "", state_school_id)
  )

df_nces_wrangled
```

### 31p2 Schools

```{r}
df_31p2_schools
colnames(df_31p2_schools)
```

#### All Schools

```{r}
# rename columns
df_31p2_schools_all_wrangled <- df_31p2_schools %>%
  rename(
    school_name = account_name,
    date_launch_core_trainings = core_training_type_launch_date,
    date_launch_all_trainings = launch_date
  ) %>%
  mutate(
    entity_code = gsub("[^[:alnum:]]", "", entity_code),
    # Core Launch
    date_launch_core_trainings = as.Date(date_launch_core_trainings, format = '%m/%d/%Y'),
    date_launch_core_year = year(date_launch_core_trainings),
    date_launch_core_month = month(date_launch_core_trainings,label=TRUE),
    # All Trainings Launch
    date_launch_all_trainings = as.Date(date_launch_all_trainings, format = '%m/%d/%Y'),
    date_launch_all_year = year(date_launch_all_trainings),
    date_launch_all_month = month(date_launch_all_trainings, label=TRUE),
    # Current Quarter Flags
    is_current_core_launch = between(date_launch_core_trainings,
                                       left=as.Date(dict_report_period[[r_quarter]][['start']], format = "%Y-%m-%d"),
                                       right=as.Date(dict_report_period[[r_quarter]][['end']], format = "%Y-%m-%d")),
    is_current_launch = between(date_launch_all_trainings,
                                      left=as.Date(dict_report_period[[r_quarter]][['start']], format = "%Y-%m-%d"),
                                      right=as.Date(dict_report_period[[r_quarter]][['end']], format = "%Y-%m-%d"))
  )
  
# Visual Checks
df_31p2_schools_all_wrangled

### NOTE: Launches and Core Launches may occur in different years and therefore Core Launch is not necessarily a subset of All Trainings Launch
table(df_31p2_schools_all_wrangled$date_launch_core_year, useNA = "always")
table(df_31p2_schools_all_wrangled$date_launch_all_year, useNA = "always")

df_31p2_schools_all_wrangled %>% 
  filter(is_current_core_launch==TRUE) %>%
  select(entity_code, is_current_core_launch, is_current_launch, date_launch_core_trainings, 
         date_launch_all_trainings)
  
```

#### \_\_Audit: 31p2 Schools Unmatched to NCES Data

```{r}

# 31p2 Schools that are unable to match to NCES student population data
audit_31p2_schools_unmatched_nces <- df_31p2_schools_all_wrangled %>%
  anti_join(x=.,
            y=df_nces_wrangled[c('state_school_id', 'students')],
            by=c('entity_code'= 'state_school_id'),
            na_matches='never')

audit_31p2_schools_unmatched_nces
```

#### \_\_Audit: 31p2 Schools Missing NCES Data

```{r}

# 31p2 Schools that successfully match to NCES data, however, student population data is missing in NCES data
audit_31p2_schools_missing_nces <- df_31p2_schools_all_wrangled %>%
  inner_join(x=.,
            y=df_nces_wrangled[c('state_school_id', 'students')],
            by=c('entity_code'= 'state_school_id'),
            na_matches='never') %>%
  filter(
    is.na(students)
  )

audit_31p2_schools_missing_nces
```

#### Launched in Reporting Quarter

```{r}

# MDE Schools Filtered by Launch in current quarter
df_31p2_schools_current_quarter <- df_31p2_schools_all_wrangled %>% 
  filter(
    is_current_core_launch == TRUE | is_current_launch == TRUE
  ) 

# Visual Check
df_31p2_schools_current_quarter

df_31p2_schools_current_quarter[df_31p2_schools_current_quarter$is_current_core_launch==TRUE,]
df_31p2_schools_current_quarter[df_31p2_schools_current_quarter$is_current_launch==TRUE,]

table(df_31p2_schools_current_quarter$date_launch_all_year, useNA = "always")
table(df_31p2_schools_current_quarter$date_launch_core_month, useNA = "always")

```

### Training Affiliations

```{r}

# Visual Check
df_affiliations
colnames(df_affiliations)

names(table(df_affiliations$training_completion_status))

table(df_affiliations$training_tier)
table(df_affiliations$training_topic)
```

```{r}
# All Affiliations from completed, qualifying traininings
df_affiliations_alltime_wrangled <- df_affiliations %>%
  rename(
    attendee_account_id = trainee_account_id,
    training_string = training_date
    ) %>%
  mutate(
    core_training_type = as.logical(core_training_type),
    # Coalesce Implementing School and School Info
    school_or_implementing_name = coalesce(aff_school, aff_implementing_school),
    school_or_implementing_code = gsub("[^[:alnum:]]", "", coalesce(aff_school_code, aff_implementing_school_code),),
    # Training Date
    training_date = as.Date(training_string, format = "%m/%d/%Y"),
    # Determine MDE Role based on Training and T2 Role
    mde_role = case_when(
      # Tier 1 Roles
      training_tier == 'Tier 1' & training_topic == 'Curriculum' ~ 'T1_Staff',
      # Tier 2 Roles
      training_tier == 'Tier 2' & training_topic == 'CBT & Mindfulness' & current_tier_2_role %in% c('CIT', 'Coach') ~ 'T2_CIT',
      training_tier == 'Tier 2' & training_topic == 'CBT & Mindfulness' & current_tier_2_role %in% c('SMHP') ~ 'T2_SMHP',
      # Tier 3 Roles
      training_tier == 'Tier 3' & training_topic == 'ISD/Administrator' ~ 'T3_Admin',
      training_tier == 'Tier 3' & training_topic == 'School Staff' ~ 'T3_Educator', 
      training_tier == 'Tier 3' & training_topic == 'SMHP' ~ 'T3_SMHP', 
      training_tier == 'Tier 3' & training_topic == 'Community' ~ 'T3_Community', 
      training_tier == 'Tier 3' & training_topic == 'Risk Assessment and Management' ~ 'T3_Both_Admin_SMHP',
      .default = 'No MDE Role'),
    # Flag for different Implementing School
    flag_novel_imp_school = case_when(
      !is.na(aff_school) & !is.na(aff_implementing_school) & aff_school != aff_implementing_school ~ TRUE,
      .default = FALSE,
    )
  ) %>%
  filter(
    # Qualifying training
    training_topic %in% names(dict_mde_role),
    # Exclude records before 07/01/2023
    training_date >= as.Date("07/01/2023", format = "%m/%d/%Y")
    )


# Current Quarter Affiliations from completed, qualifying traininings 
df_affiliations_current_quarter_wrangled <- df_affiliations_alltime_wrangled %>%
  filter(
    between(training_date,
            left = as.Date(dict_report_period[[r_quarter]][['start']], format = "%Y-%m-%d"),
            right = as.Date(dict_report_period[[r_quarter]][['end']], format = "%Y-%m-%d")
            )
  )

# Visual Checks
# df_affiliations_alltime_wrangled%>%arrange(training_date)
table(df_affiliations_alltime_wrangled$training_tier)
table(df_affiliations_alltime_wrangled$account_type)
table(df_affiliations_alltime_wrangled$flag_novel_imp_school, useNA="always")


# df_affiliations_current_quarter_wrangled
table(df_affiliations_current_quarter_wrangled$training_tier)
table(df_affiliations_current_quarter_wrangled$mde_role)

df_affiliations_current_quarter_wrangled %>%
  filter(training_tier=='Tier 2') %>%
  select(current_tier_2_role) %>%
  table()
```

## IV. Execute

### Number of Schools Implementing

#### Current Quarter

```{r}
# Group affiliations by school and determine which tiers of programming occured
df_n_schools_implementing_current_quarter <- df_affiliations_current_quarter_wrangled %>%
  group_by(school_or_implementing_code) %>%
  summarise(
    is_t1 = sum(training_tier=='Tier 1') > 0,
    is_t2 = sum(training_tier=='Tier 2') > 0,
    is_t3 = sum(training_tier=='Tier 3') > 0,
    n_tiers = sum(as.numeric(c(is_t1,is_t2,is_t3)))
  )

df_n_schools_implementing_current_quarter
```

```{r}
# OUTPUT: Total number of Tier 1 Schools 
n_schools_t1 <- df_n_schools_implementing_current_quarter %>%
  filter(is_t1) %>%
  nrow()

# OUTPUT: Total number of Tier 2 Schools 
n_schools_t2 <- df_n_schools_implementing_current_quarter %>%
  filter(is_t2) %>%
  nrow()

# OUTPUT: Total number of Tier 3 Schools 
n_schools_t3 <- df_n_schools_implementing_current_quarter %>%
  filter(is_t3) %>%
  nrow()

# OUTPUT: Total number of Schools implementing in any tier (Non-duplicative) 
n_schools_total <- nrow(df_n_schools_implementing_current_quarter)

# Add to KPI Table
df_mde_kpi_1a <- df_mde_kpi_init %>%
  add_row(
    kpi_name = 'n_schools_imp_q',
    tier_1 = n_schools_t1,
    tier_2 = n_schools_t2,
    tier_3 = n_schools_t3,
    any_tier = n_schools_total
  )

# Visual Check
df_n_schools_implementing_current_quarter
df_mde_kpi_1a

cat('Current Quarter: Number of Implementing 31p2 Schools\n',
    'Tier 1: ',n_schools_t1,'\n',
    'Tier 2: ',n_schools_t2,'\n',
    'Tier 3: ',n_schools_t3,'\n',
    'Any Tier: ',n_schools_total,'\n')
```

#### All-Time/Cumulative

```{r}
# Group affiliations by school and determine which tiers of programming occured
df_n_schools_implementing_cum <- df_affiliations_alltime_wrangled %>%
  group_by(school_or_implementing_code) %>%
  summarise(
    is_t1 = sum(training_tier=='Tier 1') > 0,
    is_t2 = sum(training_tier=='Tier 2') > 0,
    is_t3 = sum(training_tier=='Tier 3') > 0,
    n_tiers = sum(as.numeric(c(is_t1,is_t2,is_t3)))
  )
```

```{r}
# OUTPUT: Total number of Tier 1 Schools 
n_schools_t1_cum <- df_n_schools_implementing_cum %>%
  filter(is_t1) %>%
  nrow()

# OUTPUT: Total number of Tier 2 Schools 
n_schools_t2_cum <- df_n_schools_implementing_cum %>%
  filter(is_t2) %>%
  nrow()

# OUTPUT: Total number of Tier 3 Schools 
n_schools_t3_cum <- df_n_schools_implementing_cum %>%
  filter(is_t3) %>%
  nrow()

# OUTPUT: Total number of Schools implementing in any tier (Non-duplicative) 
n_schools_total_cum <- nrow(df_n_schools_implementing_cum)

# Add to KPI Table
df_mde_kpi_1b <- df_mde_kpi_1a %>%
  add_row(
    kpi_name = 'n_schools_imp_cum',
    tier_1 = n_schools_t1_cum,
    tier_2 = n_schools_t2_cum,
    tier_3 = n_schools_t3_cum,
    any_tier = n_schools_total_cum
  )

# Visual Check of DF
df_n_schools_implementing_cum
df_mde_kpi_1b

cat('Cumulative: Number of Implementing 31p2 Schools\n',
    'Tier 1: ',n_schools_t1_cum,'\n',
    'Tier 2: ',n_schools_t2_cum,'\n',
    'Tier 3: ',n_schools_t3_cum,'\n',
    'Any Tier: ',n_schools_total_cum,'\n')
```

### Number of Trainees

#### Current Quarter

```{r}

# OUTPUT: Frequeny table of Trainees by MDE Role Type
freq_table_trainees_q <- df_affiliations_current_quarter_wrangled %>%
  # Deduplicate (Trainee can only count once per school per tier of programming)
  select(school_or_implementing_code, attendee_account_id, mde_role) %>%
  unique() %>%
  select(mde_role) %>%
  table()

# OUTPUT: Trainees (Any Tier) | Non-duplicative
n_trainees_total_q <- length(unique(df_affiliations_current_quarter_wrangled$attendee_account_id))


# Add output to dataframe
for(x in names(freq_table_trainees_q)){
  df_mde_kpi_trainees[df_mde_kpi_trainees$mde_role == x, 'current_q'] <- freq_table_trainees_q[[x]]
  
}

df_mde_kpi_trainees[df_mde_kpi_trainees$mde_role == 'Any Training', 'current_q'] <- n_trainees_total_q

df_mde_kpi_trainees
```

#### All-Time/ Cumulative

```{r}

# OUTPUT: Frequeny table of Trainees by MDE Role Type
freq_table_trainees_cum <- df_affiliations_alltime_wrangled %>%
  # Deduplicate (Trainee can only count once per school per tier of programming)
  select(school_or_implementing_code, attendee_account_id, mde_role) %>%
  unique() %>%
  select(mde_role) %>%
  table()

# OUTPUT: Trainees (Any Tier) | Non-duplicative
n_trainees_total_cum <- length(unique(df_affiliations_alltime_wrangled$attendee_account_id))

# Add output to dataframe
for(x in names(freq_table_trainees_cum)){
  df_mde_kpi_trainees[df_mde_kpi_trainees$mde_role == x, 'cumulative'] <- freq_table_trainees_cum[[x]]
  
}

df_mde_kpi_trainees[df_mde_kpi_trainees$mde_role == 'Any Training', 'cumulative'] <- n_trainees_total_cum

df_mde_kpi_trainees
```

### Number of Students Who Gained Access

#### Current Quarter

```{r}
df_student_access_current_quarter <- df_affiliations_current_quarter_wrangled %>%
  # filter selected Tier 3 trainings and MDE Schools
  filter(
    school_or_implementing_code %in% unique(df_31p2_schools_current_quarter$entity_code) &
      !training_topic %in% c('Community', 'School Staff')
  ) %>%
  group_by(school_or_implementing_code) %>%
  summarise(
    is_t1 = sum(training_tier=='Tier 1') > 0,
    is_t2 = sum(training_tier=='Tier 2') > 0,
    is_t3 = sum(training_tier=='Tier 3') > 0,
    # Count Trainings implemented in school
    n_tiers = sum(as.numeric(c(is_t1,is_t2,is_t3)))
  ) %>%
  # Join to NCES Data
  ## Inner join to filter out unmatched schools
  inner_join(x=.,
            y=df_nces_wrangled[c('state_school_id', 'students')],
            by=c('school_or_implementing_code'= 'state_school_id'),
            na_matches='never') %>%
  mutate(
    students = as.integer(students)
  )

# OUTPUT: Tier 1 Student Access
n_t1_reach_quater <- sum(df_student_access_current_quarter$students[df_student_access_current_quarter$is_t1==TRUE])
# OUTPUT: Tier 2 Student Access
n_t2_reach_quater <- sum(df_student_access_current_quarter$students[df_student_access_current_quarter$is_t2==TRUE])
# OUTPUT: Tier 3 Student Access
n_t3_reach_quater <- sum(df_student_access_current_quarter$students[df_student_access_current_quarter$is_t3==TRUE])

# OUTPUT: Overall Reach (Non-Duplicative)
n_reach_total_quater <- sum(df_student_access_current_quarter$students)

# Add to KPI Table
df_mde_kpi_2a <- df_mde_kpi_1b %>%
  add_row(
    kpi_name = 'n_student_access_q',
    tier_1 = n_t1_reach_quater,
    tier_2 = n_t2_reach_quater,
    tier_3 = n_t3_reach_quater,
    any_tier = n_reach_total_quater
  )

# Visual Check
df_student_access_current_quarter
df_mde_kpi_2a
```

#### All-Time/Cumulative

```{r}

df_student_access_all <- df_affiliations_alltime_wrangled %>%
  # filter selected Tier 3 trainings
  filter(!training_topic %in% c('Community', 'School Staff')) %>%
  group_by(school_or_implementing_code) %>%
  summarise(
    is_t1 = sum(training_tier=='Tier 1') > 0,
    is_t2 = sum(training_tier=='Tier 2') > 0,
    is_t3 = sum(training_tier=='Tier 3') > 0,
    # Count Trainings implemented in school
    n_tiers = sum(as.numeric(c(is_t1,is_t2,is_t3)))
  ) %>%
  # Join to NCES Data
  inner_join(x=.,
            y=df_nces_wrangled[c('state_school_id', 'students')],
            by=c('school_or_implementing_code'= 'state_school_id'),
            na_matches='never') %>%
  mutate(
    students = as.integer(students)
  )

# OUTPUT: Tier 1 Student Access
n_t1_reach_cum <- sum(df_student_access_all$students[df_student_access_all$is_t1==TRUE])
# OUTPUT: Tier 2 Student Access
n_t2_reach_cum <- sum(df_student_access_all$students[df_student_access_all$is_t2==TRUE])
# OUTPUT: Tier 3 Student Access
n_t3_reach_cum <- sum(df_student_access_all$students[df_student_access_all$is_t3==TRUE])

# OUTPUT: Overall Reach (Non-Duplicative)
n_reach_total_cum <- sum(df_student_access_all$students)


# Add to KPI Table
df_mde_kpi_2b <- df_mde_kpi_2a %>%
  add_row(
    kpi_name = 'n_student_access_cum',
    tier_1 = n_t1_reach_cum,
    tier_2 = n_t2_reach_cum,
    tier_3 = n_t3_reach_cum,
    any_tier = n_reach_total_cum
  )

# Visual Check
df_student_access_all
df_mde_kpi_2b
```

## V. Finalize & Write Out Data

### Finalize Report Data

```{r}
# Student Access & Number of Schools Implementating
## Transpose data frame to match structure of report template
as.data.frame(t(df_mde_kpi_2b))

df_mde_kpi_out <- df_mde_kpi_2b

# Trainees
## Replace NA with 0
df_mde_kpi_trainee_out <- df_mde_kpi_trainees
df_mde_kpi_trainee_out[is.na(df_mde_kpi_trainee_out)] <- 0

df_mde_kpi_trainee_out
```

### Write Out

### Audits

```{r}
# 31p2 Schools Unmatched to NCES
## Write out audit if not empty
if(nrow(audit_31p2_schools_unmatched_nces)>1){
  write_csv(audit_31p2_schools_unmatched_nces, paste0(dir_out,'audit_31p2_schools_unmatched_to_nces_',r_year,'_',r_quarter,'_',date_suff,'.csv'))
}

# 31p2 Schools Missing NCES
## Write out audit if not empty
if(nrow(audit_31p2_schools_missing_nces)>1){
  write_csv(audit_31p2_schools_missing_nces, paste0(dir_out,'audit_31p2_schools_missing_nces_data_',r_year,'_',r_quarter,'_',date_suff,'.csv'))
}
```

### Ancillary Reports

```{r}
# Current Quarter Implementing Schools
write_csv(df_n_schools_implementing_current_quarter, 
          paste0(dir_out,'31p2_schools_implementing_',r_year,'_',r_quarter,'_',date_suff,'.csv'))

# "Launched" Schools with Student Access
write_csv(df_student_access_current_quarter, 
          paste0(dir_out,'31p2_students_gained_access_',r_year,'_',r_quarter,'_',date_suff,'.csv'))

# Current Quarter Qualifying Training Affiliations
write_csv(df_affiliations_current_quarter_wrangled, 
          paste0(dir_out,'31p2_training_affiliations_',r_year,'_',r_quarter,'_',date_suff,'.csv'))
```

![](data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAACgAAAAaCAYAAADFTB7LAAAAcElEQVR4Xu3OwQmAQAxE0bClWYCW5N06tM6V2YPg5CjoF/JhLoHAi6iqn9eOefUbqrYvHY0cQDLyAlKRNyARmYA0ZMLRkAlGQyaU72tkAtlim7r/vJqDUDjlKBROOQyFU2icQuMUGqfQuBEaV1XPOwEx96nYACK8+wAAAABJRU5ErkJggg== "Run Current Chunk")

### Report Data

```{r}
# Student Access & Number of Schools Implementating
write_csv(df_mde_kpi_out, paste0(dir_out,'mde_kpi_report_data_',r_year,'_',r_quarter,'_',date_suff,'.csv'))

# Trainees
write_csv(df_mde_kpi_trainee_out, paste0(dir_out,'mde_kpi_trainee_report_data_',r_year,'_',r_quarter,'_',date_suff,'.csv'))
```
